Figures to insert in text

### 2018-04-08 Chapters/Chapter02.tex
comparison w/ other implementations

@@

Our motivation was our own effort to run our models. As there is no reference implementation, we had to develop our own and run several simulations to ensure that our implementation was correct and bug-free. Thus, we had to deviate from our primary goal --- which was to test our hypothesis and explore the `ideas space' --- and to focus on the implementation itself. Furthermore, new members of our research group had to go through different source codes developed by former members.

@@

The main contribution of this work is a reference implementation which yields (i) orders of magnitude gains in performance, (ii) has several backends and operations, (iii) has been validated against the mathematical model, (iv) is cross-platform, and (v) is easily extended to test new research ideas. Our reference implementation may, hopefully, accelerate research into the model's dynamics and make it easier for readers to replicate any previous results and easily understand the source-code of the model.  Moreover, it is compatible with Jupyter notebook and researchers may share their notebooks possibly accelerating the advances in their fields \citep{shen2014interactive}.

>>>>

Consider the implementations of SDM present --- as of this writing --- on its wikipedia entry:

\begin{enumerate}
    \item APL implementation [59]

    \item LISP implementation for the Connection Machine [60]

    \item FPGA implementation \citep{silva_reconfigurable_2004}

    \item The original hardware implementation developed by NASA [4]

    \item C Binary Vector Symbols (CBVS): includes SDM implementation in C as a part of vector symbolic architecture[54] developed by EISLAB at Luleå University of Technology: http://pendicular.net/cbvs.php[55]

    \item CommonSense ToolKit (CSTK) for realtime sensor data processing developed at the Lancaster University includes implementation of SDM in C++: http://cstk.sourceforge.net/[56]

    \item Learning Intelligent Distribution Agent (LIDA) developed by Stan Franklin's lab at the University of Memphis includes implementation of SDM in Java: http://ccrg.cs.memphis.edu/framework.html

\end{enumerate}

Let us analyse these.  The Connection Machine is obsolete.  APL, while influential, is not a mainstream language in science. The NASA implementation is hardware-based, hence not open-source.

The FPGA implementation by \citet{silva_reconfigurable_2004} has yielded a fast scan of hard locations, provided one has access to the proper hardware. Their article claims a four-fold speedup over assembly language; but it does not deal with parallel processing details.  For example, it is unclear whether there was more than a single thread running on the software implementation.  Note that the framework presented here is also able to reconfigure field-programmable gate arrays, through the OpenCL heterogeneous computing platform ability to interface with Hardware Description Language and hence, reconfigure FPGAs \citep{waidyasooriya2018design}.

@@

Our motivation was our own effort to run our models. As there is no reference implementation, we had to develop our own and run several simulations to ensure that our implementation was correct and bug-free. Thus, we had to deviate from our primary goal --- which was to test our hypothesis and explore the `ideas space' --- and to focus on the implementation itself. Furthermore, new members of our research group had to go through different source code developed by former members, in different languages.

The main contribution of this work is a reference implementation which yields (i) orders of magnitude gains in performance, (ii) has several backends and operations, (iii) has been validated against the mathematical model, (iv) is cross-platform, and (v) is easily extensible to test new research ideas.

@@

Our reference implementation may, hopefully, accelerate research into the model's dynamics and make it easier for readers to replicate any previous results and easily understand the source-code of the model.  Moreover, it is compatible with Jupyter notebook and researchers may share their notebooks possibly accelerating the advances in their fields \citep{shen2014interactive}.
